\thetitle

### 2021-04-28 paper/paper.tex
update

\usepackage[table]{xcolor}
\usepackage[utf8x]{inputenc}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{amsmath}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[noend]{algpseudocode}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{array}
\usepackage[colon,round,sort]{natbib}
\usepackage{textcomp}
\usepackage{pifont}
% \usepackage{bbding}
\usepackage{comment}
\usepackage{graphicx}
\usepackage[svgpath=figures/]{svg}
\usepackage[labelfont=bf]{caption}
\captionsetup[table]{skip=5pt}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{shapes.geometric}
% \usepackage{tikz}
% \usetikzlibrary{patterns}
% \usetikzlibrary{calc}
% \usetikzlibrary{decorations.pathreplacing}
% \usetikzlibrary{shapes,arrows}
% \usetikzlibrary{shapes.geometric}
% \usetikzlibrary{arrows}

@@

\paragraph{Markov Decision Process.} The underlying MDP is unichain and looks as follows. Both,
state space $\mathcal{S}$ and action space $\mathcal{A}$ are discrete.
%
% Recall that we gproducts routed over the bottleneck machine \(M5\) are bottleneck products.
%
For the \textit{state space} we adapt the result of \citep{knollmann2013control}, which state that
the lead times ought to control the WIP level, instead of the due date reliability as changes are
directly seen. Thus, any state $s \in \mathcal{S}$ of the state space is composed of the following
information for both groups \(g\), i.e.\@ for bottleneck and non-bottleneck products:
\begin{itemize}

@@

The algorithm implicitly learns a function which maps the current state of the production
system to a lead time update and thus a release decision. In an optimal situation it does so by
multiply exploring every action for each state and assessing its economic viability.
%
Orders are released once the due date is within the interval $[t,t+\text{lead time}]$, whereas $t$
is the current period. Clearly, this yields bulk releases, meaning that either all or no orders with
the same due date and of the same product group are
released.

The \textit{action space} is composed of two decisions, the relative change of the lead times to the
currently set lead times $LT_{g} \in \{1,2,\ldots,\DDS\}$ for each product group $g$.
%
We restrict the lead time update for state $s_{t+1}$ according to the lead time $LT_{g}$ from state
$s_{t}$ by a maximum change of 1. Thus, if $LT_{g}$ is the current lead time of product group $g$
the agent can choose a lead time in $\{1,2,\ldots,\DDS\} \cap \{LT_{g}-1,LT_{g},LT_{g}+1\}$. % Put
% differently the algorithm can increase or decrease the lead time by 1 or leave it as it is, as long
% as it acts within the discrete action space given by the set $\{1,2,\ldots,\DDS\}$ for each product
% group.
A naive approach is to define one action for each combination of actions over all product groups.
Although applicable in our setup, as we aggregate the data into the groups of bottleneck and
non-bottleneck products and thus yields \(9\) actions, it simply does not scale.

\begin{figure*}[t!]
  \centering
  \input{figures/indep_agents}                      % Figure production system
  \caption{Illustration of independent agents as agent one increases the lead time}\label{fig:indep-agents}
\end{figure*}
%
Therefore, we invent and implement \textit{independent agents}, each operating on the same system
state, but choosing actions independently for the designated product group.
Figure~\ref{fig:indep-agents} illustrates the idea, where wlog. we use two agents and for simplicity
omit the reward and truncate the state to the lead times. Agent one chooses to increase the lead
time from \(3\) to \(4\). Thus, the future state, seen from agent one, depends on the probability of
agent two choosing to increase (\(\inc\)), decrease (\(\dec\)) or not change (\(\pers\)) the lead
time. Note that the Markov property the agent, that is
\(p(s_{t+1}, r_{t} \mid s_{t}, a_{t}) = p((4,\cdot), r_{t} \mid (3,3), \inc) \), is not touched by
this adaption. While for agent one the reward and future state only depends on the current state and
action taken, the corresponding probabilities for future state and reward change during the learning
process as the other agent starts to behave differently.
%
\MS[t]{independent agents, true?}This allows us to investigate the algorithms behaviour for even
larger solution spaces. In particular, this adaption enables us to present the algorithm the above
defined solution space not only on the basis of product groups \(g\), but also for each product type
\(p\). That means, the state space, as well as the action space operates on a product type basis.
Note that without independent agents this is infeasible due to \(3^{6} = 729\) possible actions.
Removing the dependency between the lead times of different product types reduces the possibilities,
and thus the number of ANN output layer nodes, to \(18\). Therefore, this is a vital adaption that
ensures scalability.

        %         We allow the agent a higher increase
        %         of the lead time, compared to the decrease, to give it the chance to react quickly to high
        %         number of
        %         incoming demand.

\paragraph*{Reward.}
In each period the agents choose actions, which when executed generate a reward while traversing to
the next period by simulating the production system. The rewards are the accumulated costs at the
end of the period consisting of the backorders, the WIP orders and the number of orders in the
FGI\@. The objective is to minimise the returned reward. Therefore, we adapt the algorithm by
swapping all maximisation functions with minimisations.

\paragraph*{Optimised Algorithm.}
Our implementation includes several optimisations, that help the algorithm in better exploring the
solution space and stabilise the learning process. These include the above discussed independent
agents that operate on the same state, \(n\)-step learning \citep{mnih2016asynchronous},
overestimating the average reward \(\avgrew^{\pol}\) and ensuring to constantly reduce the average
reward as searching for policies with higher average costs is unnecessary. Algorithm~\ref{alg:full}
depicts a detailed view on the algorithm including these extensions and with the minimisation
objective. The idea is the same as in Algorithm~\ref{alg:near}, except that the action selection
procedure is a loop over all independent agents and the implementation of the n-step logic.

% N-Step
N-step RL collects a set of consecutive experiences, in our case retrieved from the replay memory,
and connects the state values starting from the latest observed experience, such that the newly
computed state value of the corresponding experience propagates to the experience of the previous
period. This allows a faster convergence, as values bootstrap over multiple periods in contrast to
just one step.
% Overestimating
The idea behind overestimating the average reward is to constantly seek for better policies than the
currently known. We overestimate the reward by subtracting \(10\%\) of the computed average reward
\(\avgrew^{\pol}\) and an exponentially smoothed average reward of the actually returned reward
values of greedy actions. Thus, if the computed and actually observed average reward coincide, the
overestimation equals \(0\).
% Rho Minimum
Preventing an increase of the average reward with \(\avgrew_{\max}^{\pol}\) reduces the search space
and provides a methodology for constantly improving policy.

\MS[t]{(shared rho)?, (gradient clipping)?}

Furthermore, we sometimes use multiple parallel workers (parallel RL) that operate on the same
environment to collect a broader range of experiences. The experiences are stored according to the
first taken action in the n-step series. We uniformly sample over the actions to ensure each action
is constantly trained. This reduces catastrophic forgetting.

The algorithm initiation tactics is to first fill the replay memory buffer by skipping any learning
(steps \(10-25\)) until the period, that corresponds to the replay memory size, is reached. Then
for \(500\) steps the average reward is set to the last computed exponentially smoothed value to
prevent divergence due to the untrained network weight initialisation values.

@@

\paragraph*{Neural Network Setup.}
%
Due to the vast possibilities the neural network architecture was manually optimised, starting with
less stochastic systems and aiming for a coffin shape that can be used in all setups. During this
process we constantly adapted and reevaluated the best network on various production system
configurations. The resulting architecture depends on the number of features \(\anninp\) and the
number of output nodes \(\annout\), which itself depends on the number of actions
\(\acts = \size{\States}\), the independent agent configuration, and the number of functions that
are approximated. For the later, in case of the proposed algorithm this is \(2\),
\(\X^\pol_{\gamma_{0}}\) and \(\X^\pol_{\gamma_{1}}\), while deep Q-Learning only approximates the
function \(Q_{\gamma}^\pol\).
%
The resulting feedforward deep ANN architecture is given as %
\(\anninp %
\rightarrow 3 \anninp % \rightarrow \relu
\rightarrow \anninp % \rightarrow \relu
\rightarrow 2 \annout % \rightarrow \relu
\rightarrow \annout %
% \rightarrow   \leakyTanh%
\), where each arrow symbolises a fully-connected layer with a rectified linear unit (\(\relu\)) as
activation function. As output activation function we use the hyperbolic tangent function
(\(\Tanh\)), but similar to leaky \(\relu\), leak values greater than \(0.98\) (less than \(-0.98\))
with \(5\%\). The idea is that we do not want to restrict the approximations to values inside this
range, but values outside of it are less important and thus can be less precise.

The values \(\anninp\) and \(\annout\) depend on the feature extraction method. In case of an
aggregation to product groups \(g\) we have \(\anninp=180\), and due to \(6\) possible actions for
the two independent agents, \(\annout=12\).
% SpecFullyConnected 180 540 :=> SpecRelu (540,1,1) :=> SpecFullyConnected 540 180 :=> SpecRelu
% (180,1,1) :=> SpecFullyConnected 180 24 :=> SpecRelu (24,1,1) :=> SpecFullyConnected 24 12 :=>
% SpecReshape (12,1,1) (6,2,1) :=> SpecLeakyTanh 0.98 (6,2,1) :=> SpecNNil2D 6x2
In the case of the full representation using 6 independent agents the setup is \(\anninp=540\) and
\(\annout=36\).
% SpecFullyConnected 540 1620 :=> SpecRelu (1620,1,1) :=> SpecFullyConnected 1620 540 :=> SpecRelu
% (540,1,1) :=> SpecFullyConnected 540 72 :=> SpecRelu (72,1,1) :=> SpecFullyConnected 72 36 :=>
% SpecReshape (36,1,1) (18,2,1) :=> SpecLeakyTanh 0.98 (18,2,1) :=> SpecNNil2D 18x2
For the Q-Learning algorithm, which only approximates one function, the output nodes
\(\annout\) are halved for both setups.

The ANN is trained using the Adam optimiser \citep{kingma2014adam} with learning rate \(0.0001\),
and the default beta-values \(\beta_{1}=0.9\), and \(\beta_{2}=0.999\). As neural network
initialisation method we use the commonly known Xavier initialisation
\citep{glorot2010understanding}, i.e.\@ the initial value for each weight \(i\) is sampled from a
uniform distribution \(W_{l,i} \sim \Unif(-1/\sqrt{n_l},1/\sqrt{n_l})\), where \(n_{l}\) is the
number of nodes in layer \(l\).

@@

This section provides preliminary results for the described setup and gives an overview of the
current performance of the algorithm compared to the conventional static lead time setting
algorithms.

Currently we evaluate two different kinds of reward reporting as they have been proposed by
\cite{Schneckenreither2019}. They find that it is beneficial to overcome the time offset imposed by
the production system. That is, although orders are immediately released to the production system
and thus generate a response in terms of a reward to the agent, the full impact of the chosen action
takes several periods to materialise. For instance, by deciding not to release an order, which later
becomes a backorder, it is beneficial to reward the actions actually responsible for the backorder
instead of the last action (only). Thus they propose to keep track of the orders currently in the
order pool until all fully traversed through the production system and reward the actions according
to all orders in the order pool.

\begin{table}[t]
  \centering
  \begin{tabular}{|l||c|c|c|c|c|c|c|c|c|c|}
    \hline
    Parameter & $\alpha$ & $\beta$ & $\delta$ & $\gamma$ & $\epsilon$ & $p_{exp}$ & $\xi$ \\
    \hline
    Value & 0.5 & 0.15 & 0.15 & 0.15 & 0.5 & 1.0 & 0.15 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:params}Parameter Setup.}
\end{table}

The parameter setup is given in Table~\ref{tbl:params}. The parameters are exponentially decayed
with rate \(0.05\) and \(350k\) steps\footnote{The decay is defined as \(0.05 ^{(t/350k)}\), where
  \(t\) is the current period}. We implemented the deep Q-network algorithm proposed by
\cite{mnih2015human}, which is parameterised by learning rate \(\delta\) and a discount factor of
\(0.99\).

@@

>>>>

\usepackage[table]{xcolor}
\usepackage[utf8x]{inputenc}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{amsmath}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[noend]{algpseudocode}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{array}
\usepackage[colon,round,sort]{natbib}
\usepackage{textcomp}
\usepackage{pifont}
% \usepackage{bbding}
\usepackage{comment}
\usepackage{graphicx}
\usepackage[svgpath=figures/]{svg}
\usepackage[labelfont=bf]{caption}
\captionsetup[table]{skip=5pt}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{shapes.geometric}
% \usepackage{tikz}
% \usetikzlibrary{patterns}
% \usetikzlibrary{calc}
% \usetikzlibrary{decorations.pathreplacing}
% \usetikzlibrary{shapes,arrows}
% \usetikzlibrary{shapes.geometric}
% \usetikzlibrary{arrows}

@@

\paragraph{Markov Decision Process.} The underlying MDP is unichain and looks as follows. Both,
state space $\mathcal{S}$ and action space $\mathcal{A}$ are discrete.
%
% Recall that we gproducts routed over the bottleneck machine \(M5\) are bottleneck products.
%
For the \textit{state space} we adapt the result of \citet{knollmann2013control}, which state that
the lead times ought to control the WIP level, instead of the due date reliability as changes are
directly seen. Thus, any state $s \in \mathcal{S}$ of the state space is composed of the following
information for each product type \(\pt\):
\begin{itemize}

@@

The algorithm implicitly learns a function which maps the current state of the production
system to a lead time update and thus a release decision. In an optimal situation it does so by
multiply exploring every action for each state and assessing its economic viability.
%
Orders are released once the due date is within the interval $[t,t+\text{lead time}]$, whereas $t$
is the current period. Clearly, this yields bulk releases, meaning that either all or no orders with
the same due date and of the same product type are released.

The \textit{action space} is composed of two decisions, the relative change of the lead times to the
currently set lead times $LT_{g} \in \{1,2,\ldots,\DDS\}$ for each product type $\pt$.
%
We restrict the lead time update for state $s_{t+1}$ according to the lead time $LT_{g}$ from state
$s_{t}$ by a maximum change of 1. Thus, if $LT_{g}$ is the current lead time of product type $\pt$
the agent can choose a lead time in $\{1,2,\ldots,\DDS\} \cap \{LT_{g}-1,LT_{g},LT_{g}+1\}$. % Put
% differently the algorithm can increase or decrease the lead time by 1 or leave it as it is, as long
% as it acts within the discrete action space given by the set $\{1,2,\ldots,\DDS\}$ for each product
% type.
A naive approaches is to define one action for each combination of actions over all product type.
This however, due to the exponential growth, results in only being able to solve very small
production systems with only few product types. A common solution in production planning is to
aggregate the products into product groups, cf.\@ hierarchical production
planning~\citep{schneeweibeta1995hierarchical}.
%
Although applicable in our setup, if we group the products into bottleneck and non-bottleneck
products as done by \citet{schneckenreither2020order}, also this approach simply does not scale.

\begin{figure*}[t!]
  \centering
  \input{figures/indep_agents}                      % Figure production system
  \caption{Illustration of independent agents as agent one increases the lead time}\label{fig:indep-agents}
\end{figure*}
%
Therefore, in the seek of a broader solution we establish the idea of \textit{independent agents}.
Each independent agent operates on the same system state, but chooses only a part of the actual
executed action. In our case each independent agent is responsible for the lead time update of a
specific product type. To the best of the author's knowledge this is the first work to reduce the
action space in this way. Figure~\ref{fig:indep-agents} illustrates the idea, where wlog.\@ we use
two agents and for simplicity omit the reward and truncate the state to the lead times. Assume that
the first independent agent chooses to increase the lead time from \(3\) to \(4\). Thus, the future
state, seen from this agent, depends on the probability of the other independent agent choosing to
increase (\(\inc\)), decrease (\(\dec\)) or not change (\(\pers\)) the lead time. The Markov
property, that is
\(p(s_{t+1}, r_{t} \mid s_{t}, a_{t}) = p((4,\cdot), r_{t} \mid (3,3), (\inc, \cdot)) \), is not
touched by this adaption. While for the first agent the reward and future state only depends on the
current state and action taken, the corresponding probabilities for future state and reward change
during the learning process as the the agent starts to behave differently.
%
This allows us to investigate the algorithms behaviour for even larger solution spaces. In
particular, this adaption enables us to present the algorithm the above defined state space not only
on the basis of product groups, but directly for each product type \(\pt\). Note that without this
extension the problem is computationally infeasible due to \(3^{6} = 729\) possible actions.
Removing the dependency between the lead times of different product types reduces the set of
possible actions, and thus the number of ANN output layer nodes, to \(3 \cdot 6 = 18\). In
preliminary experiments on small examples we only observed a very slight increase of required steps
during training. Therefore, this is a vital adaption to ensure scalability.

\paragraph*{Reward.}
In each period the agents choose actions, which when executed generate a reward while traversing to
the next period by simulating the production system. The rewards are the accumulated costs at the
end of the period consisting of the backorders, the WIP orders and the number of orders in the
FGI\@. The objective is to minimise the returned reward. % Therefore, we adapt the algorithm by
% swapping all maximisation functions with minimisations.

\paragraph*{Optimised Algorithm.}
Our implementation includes several optimisations, that help the algorithm in better exploring the
solution space and stabilise the learning process. These include the above discussed independent
agents that operate on the same state, \(n\)-step learning \citep{mnih2016asynchronous}
% overestimating the average reward \(\avgrew^{\pol}\)
and ensuring to constantly reduce the average reward as searching for policies with higher average
costs is unnecessary. Algorithm~\ref{alg:full} depicts a detailed view on the algorithm including
these extensions and with the objective to minimise the returned rewards. The idea is the same as in
Algorithm~\ref{alg:near}, except that the action selection procedure is a loop over all independent
agents and the implementation of the n-step logic.

% N-Step: 5
\textit{N-step learning} collects a set of consecutive experiences, in our case retrieved from the
replay memory, and connects the state values starting from the latest observed experience, such that
the newly computed state value of the corresponding experience propagates to the experience of the
previous period. This allows a faster convergence, as values bootstrap over multiple periods in
contrast to just one step. The experiences are stored according to the first taken action in the
n-step series. We uniformly sample over the actions to ensure each action is constantly trained.
This adaption reduces catastrophic forgetting of already accumulated knowledge.
%
% Overestimating
% The idea behind overestimating the average reward is to constantly seek for better policies than the
% currently known. We overestimate the reward by subtracting \(10\%\) of the computed average reward
% \(\avgrew^{\pol}\) and an exponentially smoothed average reward of the actually returned reward
% values of greedy actions. Thus, if the computed and actually observed average reward coincide, the
% overestimation equals \(0\).
% Rho Minimum
% Preventing an increase of the average reward with \(\avgrew_{\max}^{\pol}\) reduces the search space
% and provides a methodology for constantly improving policy.
%
% Workers Min Exploration [0.01, 0.02, 0.03, 0.04, 0.05, 0.10, 0.15, 0.20]
Furthermore, we use \(8\) additional \textsf{worker threads} (parallel RL) that operate on the same
environment to collect a broader range of experiences~\citep[as e.g. in][]{mnih2016asynchronous}.

% Shared Rho (Yes)
The average reward value is shared and computed as average over the main agent and all workers.
% \MS[t]{shared rho}
%
%
% \MS[t]{worker min exploration, epsilon greedy exploration}
%
%
% Learning rate decay: ExponentialDecay (Just 5e-6) 0.25 100000
% Learning rate: OptAdam 0.005 0.9 0.999 1e-8 1e-3,

% Algorithms tested:
 %            AlgDQNAvgRewAdjusted 0.8 1.0 ByStateValues
 %          , AlgDQNAvgRewAdjusted 0.8 0.99 ByStateValues
 %          , AlgDQN 0.99 Exact

% Alpha: 0.01, Decay: ExponentialDecay (Just 5e-5) 0.25 50000
% AlphaRhoMin: 2e-5, Decay: ExponentialDecay (Just 2e-5) 0.25 50000
% Gamma: 0.01, Decay: ExponentialDecay (Just 1e-3) 0.25 100000
% Epsilon: 0.25, 0.25, Decay: No decay
% Exploration: 1.0, Decay: ExponentialDecay (Just 0.005) 0.25 100000
% LearnRandomAbove: 0.5
%
%
% UNUSED: Delta: 0.005, Decay: ExponentialDecay (Just 5e-4) 0.25 100000

The algorithm initiation strategy is to first fill the replay memory buffer by skipping any learning
(steps \(10-25\)) until the period, that corresponds to the replay memory size, is reached. Then for
\(500\) steps the average reward is set to the last computed exponentially smoothed value to prevent
divergence due to the untrained network weight initialisation values.

@@

\paragraph*{Neural Network Setup.}
%
Due to the vast possibilities the neural network architecture was manually optimised, starting with
less stochastic systems and aiming for a coffin shape that can be used in all setups. During this
process we constantly adapted and reevaluated the best network on various production system
configurations. The resulting architecture depends on the number of features \(\anninp\) and the
number of output nodes \(\annout\), which itself depends on the number of actions
\(\acts = \size{\States}\), the independent agent configuration, and the number of functions that
are approximated. For the later, in case of \ARA{} this is \(2\), as we represent both functions
\(\X^\pol_{\gamma_{0}}\) and \(\X^\pol_{\gamma_{1}}\) with the same neural network, while deep
Q-Learning only approximates the function \(Q_{\gamma}^\pol\).
%
The resulting feedforward deep ANN architecture is given as %
\(\anninp %
\rightarrow 1.75 \anninp % \rightarrow \relu
\rightarrow 1.5 \anninp % \rightarrow \relu
% \rightarrow 2 \annout % \rightarrow \relu
\rightarrow \annout %
% \rightarrow   \leakyTanh%
\), where each arrow symbolises a fully-connected layer with a leaky rectified linear unit
(\(\relu\)) as activation function, which leaks values smaller than \(0\) with rate \(0.02\). Note
that we explicitly do not use an output activation function. The idea is that we do not want to
restrict the approximations to values inside this range. This is especially important for
Q-Learning, as the range of the state values are difficult to forecast.

The values \(\anninp\) and \(\annout\) depend on the feature extraction method. In our case case
using 6 independent agents we gain \MS[t]{todo: check} \(\anninp=540\) and \(\annout=36\)
\MS[t]{check setup}. For the Q-Learning algorithm, which only approximates one function, the output
nodes \(\annout\) are halved. \MS[t]{what is the correct size?}

% Min-Max Scaling of input/output. Output: ScalingNetOutParameters (-800) 800 (-300) 300 (-400) 800 (-400) 800
\MS[t]{scaling of input layer} The features representing order counts are scaled using min-max
scaling with minimum \(0\) and maximum \(5\), the lead times with minimum \(0\) and maximum \(7\)
respectively.
% Output layer scaling
To further ensure smaller ANN parameter values the output is transformed using min-max scaling to
the interval \((-400, 800)\), s.t.\@ an ANN output of \(1\) represents a value of \(800\).
%
% Training Mini-Batch Size:  4
On each training step, i.e.\@ every n-step steps, randomly \(m\) sets of experiences the training
mini-batch size each consisting of n-step experiences are selected, there gradients computed and the
sum of gradients back-propagated though the worker network using Adam \citep{kingma2014adam}, where
the weight decay with parameter \(\lambda\) is implemented as presented by
\citet{loshchilov2017decoupled}.
%
% Smooth target network period: 100 with update 0.01
Every \(C\) steps the target network is updated by exponentially smoothing the parameters with rate
\(\gamma\).
%
% ANN Init
As neural network
initialisation method we use the commonly known Xavier initialisation
\citep{glorot2010understanding}, i.e.\@ the initial value for each weight \(i\) is sampled from a
uniform distribution \(W_{l,i} \sim \Unif(-1/\sqrt{n_l},1/\sqrt{n_l})\), where \(n_{l}\) is the
number of nodes in layer \(l\).
%
%

@@

This section provides results for the described setup and gives an overview of the current
performance of the algorithm compared to the conventional static lead time setting algorithms.

\MS[t]{todo} We evaluate two different kinds of reward reporting as they have been proposed by
\cite{Schneckenreither2019}. They find that it is beneficial to overcome the time offset imposed by
the production system. That is, although orders are immediately released to the production system
and thus generate a response in terms of a reward to the agent, the full impact of the chosen action
takes several periods to materialise. For instance, by deciding not to release an order, which later
becomes a backorder, it is beneficial to reward the actions actually responsible for the backorder
instead of the last action (only). Thus they propose to keep track of the orders currently in the
order pool until all fully traversed through the production system and reward the actions according
to all orders in the order pool.

\begin{table}[t]
  \centering
  \footnotesize
  \begin{tabular}{lP{1cm}P{1cm}P{1cm}P{1cm}P{1cm}P{1cm}P{1cm}P{1cm}P{1cm}}
    \toprule
    Parameter                      & $\alpha$   & $\alpha_{\max}$ & $\gamma_{0}$ & $\gamma_{1}$ & $\gamma$ & $\epsilon$ & $p_{exp}$ & $\plearn$ \\
    \midrule
    Start value                    & 0.01       & \(2^{-5}\)      & 0.8          & 0.99/1.0     & 0.01     & 0.25       & 1.0       & 0.5       \\
    Exp. Smth. Rate                & 0.25       &                 &              &              & 0.25     &            & 0.25      &           \\
    Exp. Smth. Steps in \(10^{3}\) & 50         &                 &              &              & 100      &            & 100       &           \\
    Minimum value                  & \(5^{-5}\) &                 &              &              & 0.001         &            & 0.005     &           \\
    \bottomrule
    \toprule
    Parameter                      & \multicolumn{8}{c}{Value} \\
    \midrule
    Workers Min. Exploration & \multicolumn{8}{c}{0.01, 0.02, 0.03, 0.04, 0.05, 0.10, 0.15, 0.20}\\
    Training Batch Size & \multicolumn{8}{c}{4}\\
    Target Network Update & \multicolumn{8}{c}{Exp. smooth. with rate \(\gamma\) every \(C=100\) steps}\\
    N-Step & \multicolumn{8}{c}{5}\\
    Training Mini-Batch Size & \multicolumn{8}{c}{\(m = 4\)}\\
    Adam Back-Propagation & \multicolumn{8}{c}{\(\alpha = 0.005, \beta_{1}=0.9,
                       \beta_{2}=0.999, \epsilon=10^{-8}, \lambda=0.001}\\ % OptAdam 0.005 0.9 0.999 1e-8 1e-3,
    \bottomrule
  \end{tabular}
  \caption{\label{tbl:params}Parameter Setup.}
\end{table}

The parameter setup is given in Table~\ref{tbl:params}. The parameters are exponentially decayed
with rate \(0.05\) and \(350k\) steps\footnote{The decay is defined as \(0.05 ^{(t/350k)}\), where
  \(t\) is the current period}. \MS[t]{TODO} We implemented the deep Q-network algorithm proposed by
\cite{mnih2015human},  a discount factor of
\(0.99\).

@@

% Therefore, in a current working paper I apply an enhanced state/action-value iteration version with
% ANN as function approximation on bigger sized problems, where preliminary promising results could be
% achieved. In the future I want to adapt and investigate the use of an actor-critic reinforcement
% learning version to problems from research and industry, where I plan to focus on production
% planning. We hypothesize that due to more correct state value estimations from the critic, the
% resulting policies from the actor are will outperform the currently known actor-critic algorithms.
% This would be in line with the observation of overestimated state values of standard discounted
% reinforcement learning algorithms, which lead to the development of
% extensions~\cite[]{hessel2018rainbow}. We believe that instead of developing extensions to resolve
% structurally fundamental problems a better approach is to aim for correct state value estimations,
% which will consequently lead to better policies.\\

\MS[t]{It remains to be shown that independent agents find the same (or better) policies.}
